---
title: "Module 7. Advanced Analytics for Research"
---

# Tổng quan Module

::: {.callout-tip title="Learning Outcomes"}
Sau khi hoàn thành Module 7, học viên có thể:

- Thực hiện thống kê mô tả nâng cao
- Áp dụng mô hình hồi quy nâng cao cho nhiều loại biến phụ thuộc
- Thực hiện Ridge, LASSO và Elastic Net Regression
- Hiểu logic cơ bản của SEM nâng cao
- Làm quen với Bayesian thinking
- Thực hiện Monte Carlo simulation
- Giải thích Simpson's Paradox
- Tạo biểu đồ Likert nâng cao
- Xây dựng visualization gallery bằng `ggplot2`
- Chọn đúng phương pháp phân tích theo câu hỏi nghiên cứu
:::

::: {.callout-note title="Module Logic"}
Module 7 là **Advanced Research Lab**.

Module 1–6 trả lời:

``` text
How do we analyze research data?
```

Module 7 trả lời:

``` text
How do we extend research analysis to advanced methods and publication-ready outputs?
```

Workflow:

``` text
Advanced data
↓
Advanced descriptive statistics
↓
Advanced regression
↓
Regularized regression
↓
SEM extension
↓
Bayesian thinking
↓
Monte Carlo simulation
↓
Simpson's Paradox
↓
Likert visualization
↓
Advanced ggplot2 gallery
↓
Research method selection
```
:::

------------------------------------------------------------------------

# 7.1 Load Packages and Data

::: {.callout-note title="Knowledge Notes"}
**What?**

Module 7 sử dụng một workbook dữ liệu mô phỏng công khai, phù hợp cho đào tạo phân tích nâng cao.

**Data file**

``` text
data/advance/module7_advanced_data.xlsx
```

**Why?**

Một workbook nhiều sheet giúp mỗi kỹ thuật có một dataset riêng, tránh trộn mục tiêu phân tích.
:::

## Install Packages

```{r}
#| eval: false

install.packages("tidyverse")
install.packages("readxl")
install.packages("janitor")
install.packages("broom")
install.packages("MASS")
install.packages("glmnet")
install.packages("moments")
install.packages("ineq")
install.packages("vegan")
install.packages("lavaan")
install.packages("boot")
install.packages("ggridges")
install.packages("ggalluvial")
install.packages("igraph")
install.packages("ggraph")
install.packages("patchwork")
```

## Load Core Packages

```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(broom)
library(patchwork)
```

## Set Data Path

```{r}
advanced_file <- if (file.exists("data/advance/module7_advanced_data.xlsx")) {
  "data/advance/module7_advanced_data.xlsx"
} else {
  "data/advanced/module7_advanced_data.xlsx"
}
```

## Check Available Sheets

```{r}
excel_sheets(advanced_file)
```

::: {.callout-warning title="Common Mistakes"}
Nếu Quarto báo không tìm thấy file, kiểm tra chính xác thư mục:

``` text
data/advance/module7_advanced_data.xlsx
```

khác với:

``` text
data/advanced/module7_advanced_data.xlsx
```
:::

------------------------------------------------------------------------

# 7.2 Advanced Descriptive Statistics

::: {.callout-note title="Knowledge Notes"}
**What?**

Advanced descriptive statistics mở rộng beyond mean and SD.

**Includes**

- Missing data audit
- Skewness
- Kurtosis
- Outlier screening
- Gini index
- Diversity index

**When?**

Dùng khi muốn hiểu sâu hơn về chất lượng và hình dạng dữ liệu.
:::

## Import Data

```{r}
adv_desc <- read_excel(
  advanced_file,
  sheet = "01_Advanced_Descriptive"
) |>
  clean_names()
```

## Overview

```{r}
glimpse(adv_desc)
```

## Missing Data Audit

```{r}
adv_desc |>
  summarise(
    across(
      everything(),
      ~ sum(is.na(.))
    )
  )
```

## Central Tendency and Variability

```{r}
adv_desc |>
  summarise(
    age_mean = mean(age, na.rm = TRUE),
    age_median = median(age, na.rm = TRUE),
    age_sd = sd(age, na.rm = TRUE),
    age_iqr = IQR(age, na.rm = TRUE),
    income_mean = mean(income_million_vnd, na.rm = TRUE),
    income_median = median(income_million_vnd, na.rm = TRUE),
    income_sd = sd(income_million_vnd, na.rm = TRUE),
    income_iqr = IQR(income_million_vnd, na.rm = TRUE)
  )
```

## Skewness and Kurtosis

```{r}
if (requireNamespace("moments", quietly = TRUE)) {
  tibble(
    variable = c("income_million_vnd", "hospital_cost", "wait_time_min"),
    skewness = c(
      moments::skewness(adv_desc$income_million_vnd, na.rm = TRUE),
      moments::skewness(adv_desc$hospital_cost, na.rm = TRUE),
      moments::skewness(adv_desc$wait_time_min, na.rm = TRUE)
    ),
    kurtosis = c(
      moments::kurtosis(adv_desc$income_million_vnd, na.rm = TRUE),
      moments::kurtosis(adv_desc$hospital_cost, na.rm = TRUE),
      moments::kurtosis(adv_desc$wait_time_min, na.rm = TRUE)
    )
  )
}
```

## Outlier Detection by IQR

```{r}
q1 <- quantile(adv_desc$outlier_score, 0.25, na.rm = TRUE)
q3 <- quantile(adv_desc$outlier_score, 0.75, na.rm = TRUE)
iqr_value <- IQR(adv_desc$outlier_score, na.rm = TRUE)

lower_bound <- q1 - 1.5 * iqr_value
upper_bound <- q3 + 1.5 * iqr_value

adv_desc |>
  filter(
    outlier_score < lower_bound |
      outlier_score > upper_bound
  )
```

## Gini Index

```{r}
if (requireNamespace("ineq", quietly = TRUE)) {
  ineq::Gini(adv_desc$income_million_vnd)
}
```

## Diversity Index

```{r}
diagnosis_counts <- adv_desc |>
  count(diagnosis_group)

diagnosis_counts
```

```{r}
if (requireNamespace("vegan", quietly = TRUE)) {
  tibble(
    shannon = vegan::diversity(diagnosis_counts$n, index = "shannon"),
    simpson = vegan::diversity(diagnosis_counts$n, index = "simpson")
  )
}
```

::: {.callout-tip title="Key Points"}
Advanced descriptive statistics giúp phát hiện các vấn đề mà mean và SD không thể hiện đầy đủ.
:::

------------------------------------------------------------------------

# 7.3 Advanced Regression Models

::: {.callout-note title="Knowledge Notes"}
**What?**

Advanced regression mở rộng hồi quy tuyến tính cho nhiều loại biến phụ thuộc.

**When?**

| Outcome type        | Model               |
|---------------------|---------------------|
| Binary              | Logistic regression |
| Ordinal             | Ordinal regression  |
| Count               | Poisson regression  |
| Overdispersed count | Negative binomial   |
| Continuous          | Linear regression   |
:::

## Import Data

```{r}
adv_reg <- read_excel(
  advanced_file,
  sheet = "02_Advanced_Regression"
) |>
  clean_names()
```

## Logistic Regression

```{r}
logit_model <- glm(
  adopted_ai ~ digital_readiness + leadership_support + workload + training_hours,
  data = adv_reg,
  family = binomial
)

tidy(logit_model, exponentiate = TRUE, conf.int = TRUE)
```

## Ordinal Regression

```{r}
if (requireNamespace("MASS", quietly = TRUE)) {
  ordinal_model <- MASS::polr(
    as.factor(ordinal_performance) ~ digital_readiness + leadership_support + motivation,
    data = adv_reg,
    Hess = TRUE
  )

  broom::tidy(ordinal_model, conf.int = TRUE)
}
```

## Poisson Regression

```{r}
poisson_model <- glm(
  absences_count ~ workload + job_satisfaction + training_hours,
  data = adv_reg,
  family = poisson
)

tidy(poisson_model, exponentiate = TRUE, conf.int = TRUE)
```

## Mediation Logic

```{r}
med_model_a <- lm(
  mediator_engagement ~ leadership_support,
  data = adv_reg
)

med_model_b <- lm(
  productivity_score ~ leadership_support + mediator_engagement,
  data = adv_reg
)

tidy(med_model_a)
tidy(med_model_b)
```

## Moderation Logic

```{r}
moderation_model <- lm(
  productivity_score ~ digital_readiness * moderator_autonomy,
  data = adv_reg
)

tidy(moderation_model)
```

::: {.callout-warning title="Common Mistakes"}
Không chọn mô hình chỉ vì quen dùng `lm()`.

Cần chọn mô hình theo loại biến phụ thuộc.
:::

------------------------------------------------------------------------

# 7.4 Ridge, LASSO and Elastic Net

::: {.callout-note title="Knowledge Notes"}
**What?**

Regularized regression là nhóm mô hình giúp xử lý nhiều predictors và đa cộng tuyến.

**Methods**

| Method      | Use                      |
|-------------|--------------------------|
| Ridge       | Shrinks coefficients     |
| LASSO       | Variable selection       |
| Elastic Net | Combines Ridge and LASSO |

**When?**

Dùng khi có nhiều biến dự báo, các biến tương quan cao hoặc mục tiêu là prediction.
:::

## Import Data

```{r}
reg_ml <- read_excel(
  advanced_file,
  sheet = "03_Ridge_Lasso_Elastic"
) |>
  clean_names()
```

## Prepare Matrix

```{r}
x <- reg_ml |>
  select(starts_with("x")) |>
  as.matrix()

y <- reg_ml$y_continuous
```

## Ridge Regression

```{r}
if (requireNamespace("glmnet", quietly = TRUE)) {
  ridge_cv <- glmnet::cv.glmnet(
    x = x,
    y = y,
    alpha = 0
  )

  ridge_cv$lambda.min
}
```

## LASSO Regression

```{r}
if (requireNamespace("glmnet", quietly = TRUE)) {
  lasso_cv <- glmnet::cv.glmnet(
    x = x,
    y = y,
    alpha = 1
  )

  lasso_cv$lambda.min
}
```

## Elastic Net Regression

```{r}
if (requireNamespace("glmnet", quietly = TRUE)) {
  elastic_cv <- glmnet::cv.glmnet(
    x = x,
    y = y,
    alpha = 0.5
  )

  elastic_cv$lambda.min
}
```

## LASSO Coefficients

```{r}
if (requireNamespace("glmnet", quietly = TRUE)) {
  coef(lasso_cv, s = "lambda.min")
}
```

::: {.callout-important title="Research Application"}
Regularized regression phù hợp cho các bài nghiên cứu prediction, đặc biệt khi có nhiều biến khảo sát hoặc nhiều biến hành vi.
:::

------------------------------------------------------------------------

# 7.5 Advanced SEM Overview

::: {.callout-note title="Knowledge Notes"}
**What?**

Advanced SEM mở rộng từ PLS-SEM cơ bản sang CFA, CB-SEM, multi-group SEM và measurement invariance.

**When?**

Dùng khi trọng tâm là theory testing và measurement quality.
:::

## Import SEM Data

```{r}
sem_adv <- read_excel(
  advanced_file,
  sheet = "04_SEM_Advanced"
) |>
  clean_names()
```

## CFA with lavaan

```{r}
if (requireNamespace("lavaan", quietly = TRUE)) {
  cfa_model <- '
    PE =~ pe1 + pe2 + pe3 + pe4
    EE =~ ee1 + ee2 + ee3 + ee4
    SI =~ si1 + si2 + si3 + si4
    FC =~ fc1 + fc2 + fc3 + fc4
    DR =~ dr1 + dr2 + dr3 + dr4
    TR =~ tr1 + tr2 + tr3 + tr4
    BI =~ bi1 + bi2 + bi3
    AU =~ au1 + au2 + au3
  '

  cfa_fit <- lavaan::cfa(
    cfa_model,
    data = sem_adv,
    ordered = names(sem_adv)[grepl("^(pe|ee|si|fc|dr|tr|bi|au)", names(sem_adv))]
  )

  lavaan::summary(
    cfa_fit,
    fit.measures = TRUE,
    standardized = TRUE
  )
}
```

::: {.callout-warning title="Common Mistakes"}
Không nên chuyển sang structural paths nếu measurement model chưa được đánh giá.
:::

------------------------------------------------------------------------

# 7.6 Bayesian Thinking and Monte Carlo

::: {.callout-note title="Knowledge Notes"}
**What?**

Bayesian thinking tập trung vào xác suất của tham số sau khi quan sát dữ liệu.

**Core logic**

``` text
Prior
↓
Data
↓
Posterior
```

Monte Carlo simulation dùng mô phỏng lặp lại để hiểu bất định và phân phối kết quả.
:::

## Import Data

```{r}
bayes_mc <- read_excel(
  advanced_file,
  sheet = "05_Bayesian_MonteCarlo"
) |>
  clean_names()
```

## Monte Carlo Simulation

```{r}
set.seed(123)

mc_means <- replicate(
  10000,
  mean(rnorm(100, mean = 0, sd = 1))
)

mc_results <- tibble(sample_mean = mc_means)

ggplot(mc_results, aes(x = sample_mean)) +
  geom_histogram(bins = 40) +
  labs(
    title = "Monte Carlo Simulation of Sample Means",
    x = "Sample mean",
    y = "Frequency"
  ) +
  theme_minimal()
```

## Bootstrap Confidence Interval

```{r}
set.seed(123)

bootstrap_means <- replicate(
  2000,
  mean(sample(bayes_mc$observed_mean, replace = TRUE))
)

tibble(bootstrap_mean = bootstrap_means) |>
  summarise(
    mean_bootstrap = mean(bootstrap_mean),
    lower_ci = quantile(bootstrap_mean, 0.025),
    upper_ci = quantile(bootstrap_mean, 0.975)
  )
```

::: {.callout-tip title="Key Points"}
Monte Carlo is useful when the answer is easier to simulate than to derive analytically.
:::

------------------------------------------------------------------------

# 7.7 Simpson's Paradox

::: {.callout-note title="Knowledge Notes"}
**What?**

Simpson's Paradox xảy ra khi xu hướng trong dữ liệu tổng hợp khác với xu hướng trong từng nhóm con.

**Why?**

Nó nhắc chúng ta rằng phân tích gộp có thể gây hiểu sai nếu có confounding variable.
:::

## Import Data

```{r}
simpson <- read_excel(
  advanced_file,
  sheet = "06_Simpsons_Paradox"
) |>
  clean_names()
```

## Department-level Rates

```{r}
simpson |>
  mutate(rate = admitted / applications) |>
  arrange(department, gender)
```

## Overall Rates

```{r}
simpson |>
  group_by(gender) |>
  summarise(
    total_applications = sum(applications),
    total_admitted = sum(admitted),
    overall_rate = total_admitted / total_applications,
    .groups = "drop"
  )
```

## Visualization

```{r}
ggplot(simpson, aes(x = department, y = admission_rate, fill = gender)) +
  geom_col(position = "dodge") +
  labs(
    title = "Simpson's Paradox: Admission Rate by Department and Gender",
    x = "Department",
    y = "Admission rate"
  ) +
  theme_minimal()
```

::: {.callout-warning title="Common Mistakes"}
Không nên chỉ nhìn dữ liệu gộp.

Luôn kiểm tra các nhóm con quan trọng.
:::

------------------------------------------------------------------------

# 7.8 Advanced Likert Analysis

::: {.callout-note title="Knowledge Notes"}
**What?**

Advanced Likert visualization giúp trình bày câu trả lời khảo sát theo dạng dễ đọc và phù hợp bài báo.

**Main plots**

- Horizontal stacked Likert bar
- Diverging Likert plot
- Grouped Likert plot
:::

## Import Likert Data

```{r}
likert_data <- read_excel(
  advanced_file,
  sheet = "07_Likert_Advanced"
) |>
  clean_names()
```

## Long Format

```{r}
likert_long <- likert_data |>
  pivot_longer(
    cols = starts_with("q"),
    names_to = "item",
    values_to = "response"
  ) |>
  mutate(
    response = factor(
      response,
      levels = 1:5,
      labels = c(
        "Strongly disagree",
        "Disagree",
        "Neutral",
        "Agree",
        "Strongly agree"
      )
    )
  )
```

## Horizontal Stacked Likert Bar

```{r}
likert_summary <- likert_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(percent = n / sum(n) * 100) |>
  ungroup()

ggplot(likert_summary, aes(x = percent, y = item, fill = response)) +
  geom_col() +
  labs(
    title = "Horizontal Likert-style Stacked Bar",
    x = "Percent",
    y = "Survey item",
    fill = "Response"
  ) +
  theme_minimal()
```

## Diverging Likert-style Bar

```{r}
likert_diverging <- likert_summary |>
  mutate(
    percent_signed = case_when(
      response %in% c("Strongly disagree", "Disagree") ~ -percent,
      response == "Neutral" ~ 0,
      TRUE ~ percent
    )
  )

ggplot(likert_diverging, aes(x = percent_signed, y = item, fill = response)) +
  geom_col() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Diverging Likert-style Bar",
    x = "Percent",
    y = "Survey item",
    fill = "Response"
  ) +
  theme_minimal()
```

------------------------------------------------------------------------

# 7.9 Advanced Visualization Lab with ggplot2

::: {.callout-note title="Knowledge Notes"}
**What?**

This section is a visualization gallery.

It introduces the main families of `ggplot2` figures and tidy visualization workflows.

**Important note**

It is not realistic to cover every single `ggplot2` function, but this lab covers the most important figure types used in research and reporting.
:::

## Load Visualization Datasets

```{r}
heatmap_data <- read_excel(
  advanced_file,
  sheet = "08_Visualization_Heatmap"
) |>
  clean_names()

volcano_data <- read_excel(
  advanced_file,
  sheet = "09_Visualization_Volcano"
) |>
  clean_names()

network_data <- read_excel(
  advanced_file,
  sheet = "10_Visualization_Network"
) |>
  clean_names()
```

------------------------------------------------------------------------

## 7.9.1 Histogram

```{r}
ggplot(adv_desc, aes(x = gpa)) +
  geom_histogram(bins = 30) +
  labs(
    title = "Histogram",
    x = "GPA",
    y = "Frequency"
  ) +
  theme_minimal()
```

## 7.9.2 Density Plot

```{r}
ggplot(adv_desc, aes(x = satisfaction)) +
  geom_density() +
  labs(
    title = "Density Plot",
    x = "Satisfaction",
    y = "Density"
  ) +
  theme_minimal()
```

## 7.9.3 Boxplot

```{r}
ggplot(adv_desc, aes(x = gender, y = satisfaction)) +
  geom_boxplot() +
  labs(
    title = "Boxplot",
    x = "Gender",
    y = "Satisfaction"
  ) +
  theme_minimal()
```

## 7.9.4 Violin Plot

```{r}
ggplot(adv_desc, aes(x = gender, y = satisfaction)) +
  geom_violin() +
  labs(
    title = "Violin Plot",
    x = "Gender",
    y = "Satisfaction"
  ) +
  theme_minimal()
```

## 7.9.5 Jitter Plot

```{r}
ggplot(adv_desc, aes(x = gender, y = satisfaction)) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(
    title = "Jitter Plot",
    x = "Gender",
    y = "Satisfaction"
  ) +
  theme_minimal()
```

## 7.9.6 Bar Chart

```{r}
adv_desc |>
  count(region) |>
  ggplot(aes(x = region, y = n)) +
  geom_col() +
  labs(
    title = "Bar Chart",
    x = "Region",
    y = "Count"
  ) +
  theme_minimal()
```

## 7.9.7 Horizontal Bar Chart

```{r}
adv_desc |>
  count(diagnosis_group) |>
  ggplot(aes(x = n, y = reorder(diagnosis_group, n))) +
  geom_col() +
  labs(
    title = "Horizontal Bar Chart",
    x = "Count",
    y = "Diagnosis group"
  ) +
  theme_minimal()
```

## 7.9.8 Stacked Bar Chart

```{r}
ggplot(adv_desc, aes(x = region, fill = gender)) +
  geom_bar() +
  labs(
    title = "Stacked Bar Chart",
    x = "Region",
    y = "Count",
    fill = "Gender"
  ) +
  theme_minimal()
```

## 7.9.9 Proportional Stacked Bar Chart

```{r}
ggplot(adv_desc, aes(x = region, fill = gender)) +
  geom_bar(position = "fill") +
  labs(
    title = "Proportional Stacked Bar Chart",
    x = "Region",
    y = "Proportion",
    fill = "Gender"
  ) +
  theme_minimal()
```

## 7.9.10 Scatter Plot

```{r}
ggplot(adv_desc, aes(x = income_million_vnd, y = satisfaction)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Scatter Plot",
    x = "Income",
    y = "Satisfaction"
  ) +
  theme_minimal()
```

## 7.9.11 Scatter Plot with Regression Line

```{r}
ggplot(adv_desc, aes(x = income_million_vnd, y = satisfaction)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "Scatter Plot with Regression Line",
    x = "Income",
    y = "Satisfaction"
  ) +
  theme_minimal()
```

## 7.9.12 Line Chart

```{r}
adv_desc |>
  mutate(date = as.Date(date)) |>
  group_by(date) |>
  summarise(
    mean_satisfaction = mean(satisfaction, na.rm = TRUE),
    .groups = "drop"
  ) |>
  ggplot(aes(x = date, y = mean_satisfaction)) +
  geom_line() +
  labs(
    title = "Line Chart",
    x = "Date",
    y = "Mean satisfaction"
  ) +
  theme_minimal()
```

## 7.9.13 Area Chart

```{r}
adv_desc |>
  mutate(date = as.Date(date)) |>
  group_by(date) |>
  summarise(
    claims = sum(claims_count, na.rm = TRUE),
    .groups = "drop"
  ) |>
  ggplot(aes(x = date, y = claims)) +
  geom_area(alpha = 0.6) +
  labs(
    title = "Area Chart",
    x = "Date",
    y = "Claims"
  ) +
  theme_minimal()
```

## 7.9.14 Faceted Plot

```{r}
ggplot(adv_desc, aes(x = satisfaction)) +
  geom_histogram(bins = 20) +
  facet_wrap(~ region) +
  labs(
    title = "Faceted Histogram",
    x = "Satisfaction",
    y = "Frequency"
  ) +
  theme_minimal()
```

## 7.9.15 Mean and Error Bar Plot

```{r}
adv_desc |>
  group_by(region) |>
  summarise(
    mean_satisfaction = mean(satisfaction, na.rm = TRUE),
    se_satisfaction = sd(satisfaction, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) |>
  ggplot(aes(x = region, y = mean_satisfaction)) +
  geom_col() +
  geom_errorbar(
    aes(
      ymin = mean_satisfaction - se_satisfaction,
      ymax = mean_satisfaction + se_satisfaction
    ),
    width = 0.2
  ) +
  labs(
    title = "Mean Plot with Standard Error",
    x = "Region",
    y = "Mean satisfaction"
  ) +
  theme_minimal()
```

## 7.9.16 Dot Plot

```{r}
adv_desc |>
  group_by(school) |>
  summarise(
    mean_gpa = mean(gpa, na.rm = TRUE),
    .groups = "drop"
  ) |>
  ggplot(aes(x = mean_gpa, y = reorder(school, mean_gpa))) +
  geom_point(size = 3) +
  labs(
    title = "Dot Plot",
    x = "Mean GPA",
    y = "School"
  ) +
  theme_minimal()
```

## 7.9.17 Lollipop Chart

```{r}
adv_desc |>
  group_by(school) |>
  summarise(
    mean_satisfaction = mean(satisfaction, na.rm = TRUE),
    .groups = "drop"
  ) |>
  ggplot(aes(x = mean_satisfaction, y = reorder(school, mean_satisfaction))) +
  geom_segment(aes(x = 0, xend = mean_satisfaction, yend = school)) +
  geom_point(size = 3) +
  labs(
    title = "Lollipop Chart",
    x = "Mean satisfaction",
    y = "School"
  ) +
  theme_minimal()
```

## 7.9.18 Heatmap

```{r}
ggplot(heatmap_data, aes(x = sample_id, y = feature, fill = value_z)) +
  geom_tile() +
  labs(
    title = "Heatmap",
    x = "Sample",
    y = "Feature",
    fill = "Z-score"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
```

## 7.9.19 Correlation Heatmap

```{r}
corr_vars <- adv_reg |>
  select(
    digital_readiness,
    leadership_support,
    workload,
    motivation,
    job_satisfaction,
    productivity_score
  )

corr_matrix <- cor(corr_vars, use = "pairwise.complete.obs")

corr_long <- as.data.frame(as.table(corr_matrix)) |>
  rename(
    variable_1 = Var1,
    variable_2 = Var2,
    correlation = Freq
  )

ggplot(corr_long, aes(x = variable_1, y = variable_2, fill = correlation)) +
  geom_tile() +
  geom_text(aes(label = round(correlation, 2)), size = 3) +
  labs(
    title = "Correlation Heatmap",
    x = NULL,
    y = NULL,
    fill = "r"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## 7.9.20 Volcano Plot

```{r}
ggplot(volcano_data, aes(x = log2_fold_change, y = neg_log10_p)) +
  geom_point(aes(shape = significant), alpha = 0.7) +
  geom_vline(xintercept = c(-1, 1), linetype = "dashed") +
  geom_hline(yintercept = -log10(0.05), linetype = "dashed") +
  labs(
    title = "Volcano Plot",
    x = "Log2 fold change",
    y = "-log10(p-value)",
    shape = "Significant"
  ) +
  theme_minimal()
```

## 7.9.21 Ridgeline Plot

```{r}
if (requireNamespace("ggridges", quietly = TRUE)) {
  ggplot(adv_desc, aes(x = satisfaction, y = region)) +
    ggridges::geom_density_ridges() +
    labs(
      title = "Ridgeline Plot",
      x = "Satisfaction",
      y = "Region"
    ) +
    theme_minimal()
}
```

## 7.9.22 Alluvial Plot

```{r}
if (requireNamespace("ggalluvial", quietly = TRUE)) {
  alluvial_data <- adv_desc |>
    count(region, gender, diagnosis_group)

  ggplot(
    alluvial_data,
    aes(
      axis1 = region,
      axis2 = gender,
      axis3 = diagnosis_group,
      y = n
    )
  ) +
    ggalluvial::geom_alluvium(aes(fill = region), width = 1/12) +
    ggalluvial::geom_stratum(width = 1/12) +
    ggalluvial::stat_stratum(
      geom = "text",
      aes(label = after_stat(stratum)),
      size = 3
    ) +
    scale_x_discrete(
      limits = c("Region", "Gender", "Diagnosis"),
      expand = c(.05, .05)
    ) +
    labs(
      title = "Alluvial Plot",
      y = "Count"
    ) +
    theme_minimal()
}
```

## 7.9.23 Network Plot

```{r}
if (requireNamespace("igraph", quietly = TRUE) &&
    requireNamespace("ggraph", quietly = TRUE)) {

  graph_object <- igraph::graph_from_data_frame(
    network_data,
    directed = TRUE
  )

  ggraph::ggraph(graph_object, layout = "fr") +
    ggraph::geom_edge_link(
      aes(width = weight),
      alpha = 0.4,
      arrow = grid::arrow(length = unit(3, "mm"))
    ) +
    ggraph::geom_node_point(size = 4) +
    ggraph::geom_node_text(
      aes(label = name),
      repel = TRUE
    ) +
    theme_void() +
    labs(
      title = "Network Plot"
    )
}
```

## 7.9.24 Coordinate Flip

```{r}
adv_desc |>
  count(region) |>
  ggplot(aes(x = region, y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Coordinate Flip Example",
    x = "Region",
    y = "Count"
  ) +
  theme_minimal()
```

## 7.9.25 Theme Comparison

```{r}
ggplot(adv_desc, aes(x = gpa, y = satisfaction)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm") +
  labs(
    title = "Theme Classic Example",
    x = "GPA",
    y = "Satisfaction"
  ) +
  theme_classic()
```

::: {.callout-tip title="Key Points"}
The most important `ggplot2` skills are:

- Reshape data with `pivot_longer()`
- Map variables using `aes()`
- Select appropriate `geom_*()`
- Add labels with `labs()`
- Improve readability with `theme_*()`
- Use facets for subgroup comparison
- Export figures with `ggsave()`
:::

------------------------------------------------------------------------

# 7.10 Research Publication Toolkit

::: {.callout-note title="Knowledge Notes"}
**What?**

A publication toolkit helps researchers convert analysis outputs into report-ready tables, figures and interpretations.

**Core outputs**

- Table 1
- Descriptive table
- Regression table
- SEM table
- Correlation heatmap
- Likert plot
- Figure captions
- Method selection guide
:::

## Method Selection Guide

| Research question                           | Recommended method     |
|---------------------------------------------|------------------------|
| What does the sample look like?             | Descriptive statistics |
| Are two variables associated?               | Correlation            |
| Which factors predict an outcome?           | Regression             |
| Which variables matter most for prediction? | LASSO / Elastic Net    |
| Does a theoretical model fit the data?      | SEM                    |
| How uncertain is the estimate?              | Bayesian / Bootstrap   |
| Can aggregation mislead us?                 | Simpson's Paradox      |
| How do respondents answer survey items?     | Likert visualization   |

------------------------------------------------------------------------

# Practice Exercise

::: {.callout-important title="Practice Exercise"}
Using `module7_advanced_data.xlsx`, complete:

1.  Create an advanced descriptive report.
2.  Fit one logistic regression model.
3.  Fit one LASSO model.
4.  Run one Monte Carlo simulation.
5.  Explain Simpson's Paradox.
6.  Create one horizontal Likert plot.
7.  Create five different ggplot2 figures.
8.  Create one heatmap.
9.  Create one volcano plot.
10. Write a short interpretation for each output.
:::

------------------------------------------------------------------------

# Challenge

::: {.callout-warning collapse="true" title="Challenge"}
## Task

Create a mini research analytics portfolio using at least five methods from Module 7.

Your portfolio must include:

- One advanced descriptive table
- One advanced regression model
- One regularized regression model
- One simulation
- One advanced visualization
- One interpretation paragraph
:::

::: {.callout-tip collapse="true" title="Suggested Solution"}
A strong portfolio can include:

1.  Skewness and kurtosis table
2.  Logistic regression for binary adoption
3.  LASSO for predictor selection
4.  Monte Carlo simulation of sample means
5.  Diverging Likert plot
6.  Correlation heatmap
7.  Short academic interpretation
:::

------------------------------------------------------------------------

# Mini Project 7

::: {.callout-important title="Mini Project 7"}
## Topic

Advanced Research Analytics Portfolio

## Deliverable

``` text
Module7_Advanced_Analytics_Portfolio.html
```

## Required sections

1.  Advanced descriptive statistics
2.  Advanced regression model
3.  Ridge/LASSO/Elastic Net analysis
4.  Monte Carlo simulation
5.  Simpson's Paradox interpretation
6.  Likert visualization
7.  Advanced ggplot2 visualization gallery
8.  Method selection guide
9.  Academic interpretation
10. Reflection on when to use each method
:::

------------------------------------------------------------------------

# Key Takeaways

::: {.callout-tip title="Key Points"}
- Advanced analytics should be selected based on the research question, not trendiness.
- Ridge, LASSO and Elastic Net are useful for prediction and many predictors.
- Bayesian thinking focuses on uncertainty and probability.
- Monte Carlo simulation helps understand uncertainty through repeated sampling.
- Simpson's Paradox shows why subgroup analysis matters.
- Likert visualization is essential for survey research.
- `ggplot2` can produce almost all common research figures when combined with tidy data.
- Publication-ready research requires good methods, good figures and careful interpretation.
:::

------------------------------------------------------------------------

# What Next?

::: {.callout-note title="What Next?"}
After Module 7, learners should be able to design their own research analytics workflow.

Recommended next steps:

1.  Choose a research question.
2.  Identify the outcome variable.
3.  Select a suitable method.
4.  Run the analysis.
5.  Create publication-ready figures.
6.  Write an interpretation.
7.  Document the full workflow in Quarto.
:::
